---
title: "RedWine_202211"
author: "Stephan"
date: "2022-11-24"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}

```

Install all needed libraries and load them

```{r load the ggplot graphics package and the others}
library(ggplot2)
library(dplyr)
library(reshape2)
library(tidyr)
library(gridExtra)
library(ggplot2)
library(alr4)
library(GGally)
library(ggplot2)
library(GGally)
library(scales)
library(memisc)
```

Import the data set

```{r echo=FALSE, Load_the_Data}
# Load the Data
getwd()
red_wine <- read.csv("wineQualityReds.csv")

```

# Uni-variate Plots Section

Determine the class, structure of data set as well as a summary.

Print a head of the data to see what it looks like.

```{r echo=FALSE, Univariate_Plots}

###Structure of Data from Red Wine Quality
class(red_wine)
str(red_wine)
summary(red_wine)
head(red_wine)

```

Draw different graphs to show the relationship of all the determining factors to the quality of the wine.

```{r}
ggplot(red_wine,aes(x = quality))+
  geom_histogram()+
  facet_wrap(~quality, scales = 'free_y')

ggplot(red_wine, aes(x = pH))+
  geom_histogram(binwidth = 0.07, fill = '#1234DC', color = 'red')+
  facet_wrap(~quality, scales = 'free_y')

ggplot(red_wine, aes(x = fixed.acidity))+
  geom_histogram(binwidth = 0.05, fill = '#1234DC', color = 'red')+
  facet_wrap(~quality, scales = 'free_y')

ggplot(red_wine, aes(x = volatile.acidity))+
  geom_histogram(binwidth = 0.01, fill = '#1234DC', color = 'red')+
  facet_wrap(~quality, scales = 'free_y')

ggplot(red_wine, aes(x = citric.acid))+
  geom_histogram(binwidth = 0.01, fill = '#1234DC', color = 'red')+
  facet_wrap(~quality, scales = 'free_y')

ggplot(red_wine, aes(x = residual.sugar))+
  geom_histogram(binwidth = 0.08, fill = '#1234DC', color = 'red')+
  facet_wrap(~quality, scales = 'free_y')

 ggplot(red_wine, aes(x = chlorides))+
  geom_histogram(binwidth = 0.005, fill = '#1234DC', color = 'red')+
  facet_wrap(~quality, scales = 'free_y')
 
 ggplot(red_wine, aes(x = free.sulfur.dioxide))+
  geom_histogram(fill = '#1234DC', color = 'red')+
  facet_wrap(~quality, scales = 'free_y')
 
 ggplot(red_wine, aes(x = total.sulfur.dioxide))+
  geom_histogram(fill = '#1234DC', color = 'red')+
  facet_wrap(~quality, scales = 'free_y')
 
 ggplot(red_wine, aes(x = density))+
  geom_histogram(binwidth = 0.0005, fill = '#1234DC', color = 'red')+
  facet_wrap(~quality, scales = 'free_y')
 
 ggplot(red_wine, aes(x = sulphates))+
  geom_histogram(binwidth = 0.01, fill = '#1234DC', color = 'red')+
  facet_wrap(~quality, scales = 'free_y')
 
 ggplot(red_wine, aes(x = alcohol))+
  geom_histogram(binwidth = 0.1, fill = '#1234DC', color = 'red')+
  facet_wrap(~quality, scales = 'free_y')
 
 

summary(red_wine$quality)

```

Calculate the amount of wines above and below the mean and median

```{r}

###Sum above and below Mean and Medain Quality
sum(red_wine$quality)

sum(red_wine$quality> mean(red_wine$quality))
sum(red_wine$quality< mean(red_wine$quality))

sum(red_wine$quality> median(red_wine$quality))
sum(red_wine$quality< median(red_wine$quality))
```

3 different graphs:

1 - quality vs pH with geom point / scatter plot\
2 - quality vs pH with geom jitter plot\
3 - quality vs alcohol with jitter plot and line chart

```{r}

ggplot(aes(x = quality, y = pH),data = red_wine)+
  geom_point(alpha = 1/10)

ggplot(aes(x = quality, y = pH),data = red_wine)+
  geom_jitter(alpha = 1/10)

ggplot(aes(x = quality, y = alcohol),data = red_wine)+
  geom_jitter(alpha = 1/5, color = "red")+
  geom_line(stat = "summary", color = "blue")


```

4 x violin plots between quality and 4 influencing elements:

-alcohol\
-citric.acid\
-sulphates\
-pH

```{r}

library(gridExtra)
library(grid)


plot1 <- ggplot(aes(x = quality, y = alcohol, group = quality),data = red_wine)+
            geom_line()+
            geom_violin(alpha = 1/3, color = "blue", fill = '#1234DC' )+
            geom_jitter(alpha = 1/5, color = "red")
            
  
  

plot2 <- ggplot(aes(x = quality, y = citric.acid, group = quality),data = red_wine)+  
            geom_violin(alpha = 1/10, color = "blue", fill = '#1234DC' )+
            geom_jitter(alpha = 1/5, color = "red")


plot3 <- ggplot(aes(x = quality, y = sulphates, group = quality),data = red_wine)+
            geom_violin(alpha = 1/10, color = "blue", fill = '#1234DC' )+
            geom_jitter(alpha = 1/5, color = "red")

plot4 <- ggplot(aes(x = quality, y = pH, group = quality),data = red_wine)+
            geom_violin(alpha = 1/10, color = "blue", fill = '#1234DC' )+
            geom_jitter(alpha = 1/5, color = "red")


grid.arrange(plot1, plot2 ,plot3, plot4, ncol = 4)
```

4 x box plots between quality and 4 influencing elements:

-alcohol\
-citric.acid\
-sulphates\
-pH

```{r}
library(gridExtra)
library(grid)


plot5 <- ggplot(aes(x = quality, y = alcohol, group = quality),data = red_wine)+
            geom_boxplot(alpha = 1/3, color = "blue", fill = '#1234DC' )+
            geom_jitter(alpha = 1/5, color = "red")

plot6 <- ggplot(aes(x = quality, y = citric.acid, group = quality),data = red_wine)+  
            geom_boxplot(alpha = 1/10, color = "blue", fill = '#1234DC' )+
            geom_jitter(alpha = 1/5, color = "red")

plot7 <- ggplot(aes(x = quality, y = sulphates, group = quality),data = red_wine)+
            geom_boxplot(alpha = 1/10, color = "blue", fill = '#1234DC' )+
            geom_jitter(alpha = 1/5, color = "red")

plot8 <- ggplot(aes(x = quality, y = pH, group = quality),data = red_wine)+
            geom_boxplot(alpha = 1/10, color = "blue", fill = '#1234DC' )+
            geom_jitter(alpha = 1/5, color = "red")


grid.arrange(plot5, plot6 ,plot7, plot8, ncol = 4)
```

Two graphs showing the relationship between:

1- Quality vs Alcohol\
2- Quality vs Volatile Acidity

```{r}
ggplot(aes(y = alcohol, x = quality), data = red_wine) +
  geom_point(alpha = 1/20)+
  geom_smooth(method = 'lm', color = 'green')

ggplot(aes(y = volatile.acidity, x = quality), data = red_wine) +
  geom_point(alpha = 1/20)+
  geom_smooth(method = 'lm', color = 'red')

```






